Dynein project log

### 2016-09-30 thesis_stuff/thesis_stuff.tex
make figure use references

These figures show different measurements for equilibrium angles from the data in this paper:\\

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Post_powerstroke_tomography.jpg}
    \caption{Post-powerstroke equilibrium angles from EM tomography.}
  \end{minipage}
  \hspace{5mm}
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
    \caption{Pre-powerstroke equilibrium angles from EM tomography. Note: Ignore binding angle, the MTBD shouldn't actually be bound to MT.}
  \end{minipage}
  \label{fig:em_tomography_eq_angles}
\end{figure}

>>>>

Figure~\ref{fig:em_tomography_eq_angles} shows different measurements
for equilibrium angles from the data in this paper.
\begin{figure}[h!]
  \centering
  \includegraphics[width=.45\textwidth]{../figures/Post_powerstroke_tomography.jpg}
  \includegraphics[width=.45\textwidth]{../figures/Pre_powerstroke_tomography.jpg}
  \caption{Post- and Pre-powerstroke equilibrium angles from EM tomography. Note: Ignore binding angle, the MTBD shouldn't actually be bound to MT.}
  \label{fig:em_tomography_eq_angles}
\end{figure}
